---
title: "Task1"
author: "Hoda"
date: "2023-01-22"
output: pdf_document
---
```{r setup, include=FALSE} 
knitr::opts_chunk$set(warning = FALSE, message = FALSE) 
```

## TASK 1



```{r data, echo=FALSE}
library(readxl)
```

## Barplot of number of sold PIZZA from 2017 - 2021

In the following the barplot of #PIZZA for Temperature,SUN,Price.offer and Precipitation can be see.


```{r years, echo=FALSE}
data = read.csv('data.csv')
#my_data %>% drop_na()
Pizza = data$Pizza
Year2017 = data[1:52,]
Year2018 = data[53:104,]
Year2019 = data[105:157,]
Year2020 = data[158:209,]
Year2021 = data[210:dim(data)[1],]
```
## PIZZA , Temperature
```{r  echo=FALSE }

years = c("2017", "2018", "2019", "2020", "2021")
colors = c("blue", "green", "red", "purple", "orange")
par(mfrow = c(1, 2))

# Create the first bar plot
barplot(c(sum(Year2017$Pizza), sum(Year2018$Pizza), sum(Year2019$Pizza), sum(Year2020$Pizza), sum(Year2021$Pizza)), 
        names.arg = years, 
        xlab = "Year", ylab = "Number of Sold Pizza",col=colors)

# Create the second bar plot
barplot(c(mean(Year2017$Temperature), mean(Year2018$Temperature), mean(Year2019$Temperature), mean(Year2020$Temperature), mean(Year2021$Temperature)), 
        names.arg = years, 
        xlab = "Year", ylab = "Temperature mean",col=colors)

#####################################################################################
```

## PIZZA , Sun

```{r  echo=FALSE }
par(mfrow = c(1, 2))
barplot(c(sum(Year2017$Pizza), sum(Year2018$Pizza), sum(Year2019$Pizza), sum(Year2020$Pizza), sum(Year2021$Pizza)), 
        names.arg = years, 
        xlab = "Year", ylab = "Number of Sold Pizza",col=colors)

# Create the second bar plot
barplot(c(mean(Year2017$Sun), mean(Year2018$Sun), mean(Year2019$Sun), mean(Year2020$Sun), mean(Year2021$Sun)), 
        names.arg = years, 
        xlab = "Year", ylab = "Sun mean",col=colors)
```

## PIZZA , Price.offer

```{r}
par(mfrow = c(1, 2))
barplot(c(sum(Year2017$Pizza), sum(Year2018$Pizza), sum(Year2019$Pizza), sum(Year2020$Pizza), sum(Year2021$Pizza)), 
        names.arg = years, 
        xlab = "Year", ylab = "Number of Sold Pizza",col=colors)

# Create the second bar plot
barplot(c(mean(Year2017$Price.offer), mean(Year2018$Price.offer), mean(Year2019$Price.offer), mean(Year2020$Price.offer), mean(Year2021$Price.offer)), 
        names.arg = years, 
        xlab = "Year", ylab = "Price.offer mean",col=colors)
```

## PIZZA , Precipitation

```{r  echo=FALSE}
par(mfrow = c(1, 2))
# Create the first bar plot
barplot(c(sum(Year2017$Pizza), sum(Year2018$Pizza), sum(Year2019$Pizza), sum(Year2020$Pizza), sum(Year2021$Pizza)), 
        names.arg = years, 
        xlab = "Year", ylab = "Number of Sold Pizza",col=colors)

# Create the second bar plot
barplot(c(mean(Year2017$Precipitation), mean(Year2018$Precipitation), mean(Year2019$Precipitation), mean(Year2020$Precipitation), mean(Year2021$Precipitation)), 
        names.arg = years, 
        xlab = "Year", ylab = "Precipitation mean",col=colors)
```

## Histogram of sold PIZZA from 2017 - 2021
```{r echo=FALSE}
# Set the layout to 4 rows and 1 column
par(mfrow = c(2, 3))

# Create a histogram of the data for Year 2017 with frequency on the y-axis
hist(Year2017$Pizza,
     main = "Histogram of Year 2017", xlab = "PIZZA", ylab = "Frequency",
     col = "blue")

# Create a histogram of the data for Year 2018 with frequency on the y-axis
hist(Year2018$Pizza, 
     main = "Histogram of Year 2018", xlab = "PIZZA", ylab = "Frequency",
     col = "green", border = "green")

# Create a histogram of the data for Year 2019 with frequency on the y-axis
hist(Year2019$Pizza,
     main = "Histogram of Year 2019", xlab = "PIZZA", ylab = "Frequency",
     col = "red", border = "red")

# Create a histogram of the data for Year 2020 with frequency on the y-axis
hist(Year2020$Pizza,  
     main = "Histogram of Year 2020", xlab = "PIZZA", ylab = "Frequency",
     col = "purple", border = "purple")

# Create a histogram of the data for Year 2021 with frequency on the y-axis
hist(Year2021$Pizza, 
     main = "Histogram of Year 2021", xlab = "PIZZA", ylab = "Frequency",
     col = "orange", border = "orange")
```

## Histogram of Temperature from 2017 - 2021

```{r echo=FALSE}
##############################################################################################
# Set the layout to 4 rows and 1 column
par(mfrow = c(2, 3))

# Create a histogram of the data for Year 2017 with frequency on the y-axis
hist(Year2017$Temperature,
     main = "Histogram of Year 2017", xlab = "Temperature", ylab = "Frequency",
     col = "blue",breaks = 50)

# Create a histogram of the data for Year 2018 with frequency on the y-axis
hist(Year2018$Temperature, 
     main = "Histogram of Year 2018", xlab = "Temperature", ylab = "Frequency",
     col = "green", border = "green",breaks = 50)

# Create a histogram of the data for Year 2019 with frequency on the y-axis
hist(Year2019$Temperature,
     main = "Histogram of Year 2019", xlab = "Temperature", ylab = "Frequency",
     col = "red", border = "red",breaks = 50)

# Create a histogram of the data for Year 2020 with frequency on the y-axis
hist(Year2020$Temperature,  
     main = "Histogram of Year 2020", xlab = "Temperature", ylab = "Frequency",
     col = "purple", border = "purple",breaks = 50)

# Create a histogram of the data for Year 2021 with frequency on the y-axis
hist(Year2021$Temperature, 
     main = "Histogram of Year 2021", xlab = "Temperature", ylab = "Frequency",
     col = "orange", border = "orange",breaks = 50)

###########################################################################################
```

## Histogram of Sun from 2017 - 2021

```{r echo=FALSE}
##############################################################################################
# Set the layout to 4 rows and 1 column
par(mfrow = c(2, 3))

# Create a histogram of the data for Year 2017 with frequency on the y-axis
hist(Year2017$Sun,
     main = "Histogram of Year 2017", xlab = "Sun", ylab = "Frequency",
     col = "blue",breaks = 50)

# Create a histogram of the data for Year 2018 with frequency on the y-axis
hist(Year2018$Sun, 
     main = "Histogram of Year 2018", xlab = "Sun", ylab = "Frequency",
     col = "green", border = "green",breaks = 50)

# Create a histogram of the data for Year 2019 with frequency on the y-axis
hist(Year2019$Sun,
     main = "Histogram of Year 2019", xlab = "Sun", ylab = "Frequency",
     col = "red", border = "red",breaks = 50)

# Create a histogram of the data for Year 2020 with frequency on the y-axis
hist(Year2020$Sun,  
     main = "Histogram of Year 2020", xlab = "Sun", ylab = "Frequency",
     col = "purple", border = "purple",breaks = 50)

# Create a histogram of the data for Year 2021 with frequency on the y-axis
hist(Year2021$Sun, 
     main = "Histogram of Year 2021", xlab = "Sun", ylab = "Frequency",
     col = "orange", border = "orange",breaks = 50)

###########################################################################################
```

## Histogram of Precipitation from 2017 - 2021


```{r echo=FALSE}
##############################################################################################
# Set the layout to 4 rows and 1 column
par(mfrow = c(2, 3))

# Create a histogram of the data for Year 2017 with frequency on the y-axis
hist(Year2017$Precipitation,
     main = "Histogram of Year 2017", xlab = "Precipitation", ylab = "Frequency",
     col = "blue",breaks = 50)

# Create a histogram of the data for Year 2018 with frequency on the y-axis
hist(Year2018$Precipitation, 
     main = "Histogram of Year 2018", xlab = "Precipitation", ylab = "Frequency",
     col = "green", border = "green",breaks = 50)

# Create a histogram of the data for Year 2019 with frequency on the y-axis
hist(Year2019$Precipitation,
     main = "Histogram of Year 2019", xlab = "Precipitation", ylab = "Frequency",
     col = "red", border = "red",breaks = 50)

# Create a histogram of the data for Year 2020 with frequency on the y-axis
hist(Year2020$Temperature,  
     main = "Histogram of Year 2020", xlab = "Precipitation", ylab = "Frequency",
     col = "purple", border = "purple",breaks = 50)

# Create a histogram of the data for Year 2021 with frequency on the y-axis
hist(Year2021$Precipitation, 
     main = "Histogram of Year 2021", xlab = "Precipitation", ylab = "Frequency",
     col = "orange", border = "orange",breaks = 50)

###########################################################################################
```

## Histogram of Price.offer from 2017 - 2021


```{r echo=FALSE}
##############################################################################################
# Set the layout to 4 rows and 1 column
par(mfrow = c(2, 3))

# Create a histogram of the data for Year 2017 with frequency on the y-axis
hist(Year2017$Price.offer,
     main = "Histogram of Year 2017", xlab = "Price.offer", ylab = "Frequency",
     col = "blue",breaks = 50)

# Create a histogram of the data for Year 2018 with frequency on the y-axis
hist(Year2018$Price.offer, 
     main = "Histogram of Year 2018", xlab = "Price.offer", ylab = "Frequency",
     col = "green", border = "green",breaks = 50)

# Create a histogram of the data for Year 2019 with frequency on the y-axis
hist(Year2019$Price.offer,
     main = "Histogram of Year 2019", xlab = "Price.offer", ylab = "Frequency",
     col = "red", border = "red",breaks = 50)

# Create a histogram of the data for Year 2020 with frequency on the y-axis
hist(Year2020$Price.offer,  
     main = "Histogram of Year 2020", xlab = "Price.offer", ylab = "Frequency",
     col = "purple", border = "purple",breaks = 50)

# Create a histogram of the data for Year 2021 with frequency on the y-axis
hist(Year2021$Temperature, 
     main = "Histogram of Year 2021", xlab = "Temperature", ylab = "Frequency",
     col = "orange", border = "orange",breaks = 50)

###########################################################################################
```

## creating the model

###  Preprocessing and split to train and test

```{r echo=TRUE, include= TRUE}


data = read.csv('data.csv')
summary(data)

df2=data[, -c(1)]
#remove 0 column
temp = c("Campaign.14", "Campaign.15", "Campaign.16","Campaign17","Campaign.18" ) 
df2 = df2[ ,! names(df2) %in% temp]
df3=as.data.frame(scale(df2))

data=df3
for(i in 1:ncol(data)) {
  data[is.na(data[,i]), i] <- min(data[,i], na.rm = TRUE)
}

# Replace missing values with the median of the column
missing_rows <- sapply(data, function(x) any(is.na(x)))
missing_rows_index <- which(missing_rows)


n=dim(data)[1]
set.seed(12345) 
id=sample(1:n, floor(n*0.7))

# split to train and test

train=data[id,] 
test=data[-id,] 
trainX=as.matrix(train[,-1])
testX=as.matrix(test[,-1])

```

### First linear regression model

```{r}
m1=lm(Pizza~., data=train)
summary(m1)
cat('mean square error on train set = ', mean((train$Pizza-predict(m1,train))^2,na.rm=TRUE),'\n')  
cat('mean square error on test set = ', mean((test$Pizza-predict(m1,test))^2,na.rm=TRUE),'\n')  
qqnorm(residuals(m1))
qqline(residuals(m1))

```

### Second linear model, exclude competitor

```{r}
#model2
model <- lm(Pizza ~ Price.offer +Temperature +Precipitation + Sun + Christmas + New.year + X17th.of.May...National.day + Easter + 
              Kr..Himmelfart..Ascension.day. + Pinse..pentecost. + Summer.vacation + Campaign.1 + 
              Campaign.2 + Campaign.3 + Campaign.4 + Campaign.5 + Campaign.6 + Campaign.7 + 
              Campaign.8 + Campaign.9 + Campaign.10 + Campaign.11 + Campaign.12 + Campaign.13 , data = train)
summary(model)
cat('mean square error on train set = ', mean((train$Pizza-predict(model,train))^2,na.rm=TRUE),'\n')  

cat('mean square error on test set = ', mean((test$Pizza-predict(model,test))^2,na.rm=TRUE),'\n')  

 
qqnorm(residuals(model))
qqline(residuals(model))
```

#### Finiding the most important feature among:  Price.offer, Temperature, Precipitation, Sun

```{r echo=TRUE}
###############################################################

lm2 = lm(Pizza ~ Price.offer+Temperature+Precipitation + Sun,data = train)
summary(lm2)
cat('mean square error on train set = ', mean((train$Pizza-predict(lm2,train))^2,na.rm=TRUE),'\n')  

cat('mean square error on test set = ', mean((test$Pizza-predict(lm2,test))^2,na.rm=TRUE),'\n')  

qqnorm(residuals(lm2))
qqline(residuals(lm2))
#################################################################
```

Based on the coef Price.Offer is the most important one.

## LASSO and Ridge Regression model

```{r echo=TRUE}
library(glmnet)
model0=glmnet(trainX, train$Pizza, alpha=1,family="gaussian")
plot(model0, xvar="lambda", label=TRUE)

model1=glmnet(trainX, train$Pizza, alpha=0,family="gaussian")
plot(model1, xvar="lambda", label=TRUE)



set.seed(12345)
model=cv.glmnet(trainX, train$Pizza, alpha=1,family="gaussian")
model$lambda.min
plot(model)


mB=glmnet(trainX, train$Pizza, alpha=1,family="gaussian", lambda = model$lambda.min)
cat('mean square error on test set = ', mean((test$Pizza-predict(mB,testX))^2),'\n')  
plot(predict(mB, testX),test$Pizza,ylab = 'TRUE Value', xlab = 'Predicted Value',main = 'Quality of predicted Prediction')

```

### The most important featurs
 
```{r}

coefs <- coef(mB, s = "lambda.min")

important_feature_indices <- order(abs(coefs), decreasing = TRUE)[1:6]
#Feature_name_most = names(train)
Feature_name_most = coefs@Dimnames[[1]]
important_features <- Feature_name_most[important_feature_indices]
cat('The most important features: ')

important_features_df = data.frame(data = t(coefs[important_feature_indices]) )
names(important_features_df) = important_features
print(important_features_df)
```
Easter and Sun has negative effect in selling the highest number of PIZZA.


### Pie chart of 

```{r}
values <- c(0.79255940,0.17012066,0.08354925,0.07847286)
labels <- c('Price.offer','Campaign.5','Campaign.2','Competitor.4')
pie(values, labels = paste0(round(values/sum(values)*100,2),"%"), main = "2D Percentage Pie Chart", col = rainbow(6), init.angle = 90, clockwise = TRUE, cex = 0.8)
legend("topright",legend=labels, cex=0.8,fill=rainbow(6))



```



### The least important Features

```{r}
zero_coef_indices_least <- which(coefs == 0)
Feature_name = coefs@Dimnames[[1]]
zero_coef_features <- Feature_name[zero_coef_indices_least]
cat('The least important features: ')
print(zero_coef_features)

```

